25 years of Social Work Research

### 2015-02-22 dataCleaning.Rmd
Code for Arete journal titles

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)
```

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

>>>>

#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Aretê",                                   #Spelling difference
      "Arete",
              full.df$record)
```

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "Arete: Revista de Filosofia")
